Meta-analysis of fungicide application timing for powdery mildew management

### 2020-02-05 04_Prep_data.Rmd
Adding some reporting messages
add explaination of the sequence of AUDPC x grain yeild graphs

@@

head(slim_PM_dat)
```

@@

>>>>

# Calculate AUDPC using final severity and first sign of disease - 7 days
source("R/AUDPC_for_single_obs.R") 
```

@@

@@

This sequence of graphs show that AUDPC and disease incidence does not impact on yields if the season is a low yielding, ie lower than 1 tonne per hectare.  
The higher the yield the greater greater the influence on the disease on the yield especially if the crop is high yielding and a large AUDPC.
